%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

% \profilepic{seon.jpg} % Profile picture
\cvname{Séon O'Shannon} % Your name
\cvjobtitle{\normalsize{\centerline{Developer | Manager}}} % Job title/career

\cvaddress{Reno, NV} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{+1 (775) 354-4343} % Phone number
\cvsite{https://eons.llc} % Personal website
\cvmail{seon@eons.llc} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 ABOUT ME
%----------------------------------------------------------------------------------------

\aboutme{From business to biotech to de novo AI to cloud native software, my breadth of experience allows me to easily cross disciplines and bring people together. Building strong teams and resilient communities is something I continuously strive for. Whether I get to learn a new programming language, backdoor broken servers, design hardware, or build new organisms, I'm always excited to dig into interesting problems with good people and come back with novel solutions. I believe we have a responsibility to work together to leave this world better than we found it.}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{%
	{\textbf{Experiment Design \& Debugging}/5.3},%
	{\textbf{Security}/4},%
	{\textbf{Git / Version Control}/3},%
	{\textbf{Devops + CI/CD}/3.8},%
	{\textbf{Windows}/4.5},%
	{\textbf{Linux}/5.5},%
	{\textbf{Hardware \& Electrical Engineering}/2},%
	{\textbf{Embedded Systems}/2.3},%
	{\textbf{Cloud Architecture}/4.5},%
    {\textbf{Web (PHP, JS, CSS, HTML)}/5.0},%
	{\textbf{Python}/5.2},%
	{\textbf{C++}/5.8},%
	{\textbf{Leadership}/4.2}%
}

%------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6
%\skillstext{{Hacker/},{Scientist/},{Manager/}}

%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 INTERESTS
%----------------------------------------------------------------------------------------

%\section{Interests}
%
%I'm interested in working on any difficult problems and learning as much as I can.
%Generally, this includes any kind of engineering and theory of biology through math.


%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
	\twentyitem{2022-now}{Senior Software Engineer}{\textbf{Zywave}}{%
		For Zywave, I help lead a team focused on delivering a great user experience for comparative insurance quoting. This work includes web development, solutions architecture, data management, and devops.%
	}
	\twentyitem{2021-2022}{Solutions Architect}{\textbf{AOE Greens}}{%
		For AOE Greens, I provided the custom software and cloud infrastructure for controlling hydroponics hardware through a secure web interface. Besides business strategy, the CEO and I collaborated on the design of hardware, circuits, software, and UI/UX for a fully custom IoT solution.%
	}
	\twentyitem{2020-now}{Founder \& CEO}{\textbf{eons LLC}}{%
		For my own business, I architect, implement, maintain, and secure our cloud environment and frameworks for ops, AI, and data management. My work includes everything from hardware assembly through vpn \& firewall implementation to Kubernetes management and web development. I also handle our budgets and keep our clients happy.%
	}
	\twentyitem{2017-2021}{Research Associate}{\textbf{Zeakal}}{%
		I worked on a genetic engineering pipeline and managed other personnel, equipment, greenhouses, labs, and reagents. Using both Excel and Python, I wrote and mathematically verified software for automating the digestion of experimental data, enabling faster time-to-results across numerous studies. For collaboration with our global team, I built and hosted data servers for research results.%
	}
	\twentyitem{2015-2019}{Lead Software Engineer}{\textbf{Brain2Bot}}{%
		Using C++, Qt, \& novel neuroscience I designed, developed, and deployed a cross-platform software solution for building brains. I built wired, and wrote drivers for PWM, SPI, \& I2C modules to create robot pets.%
	}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2013-2017}{B.S. Biochemistry \& Molecular Biology}{University of Nevada, Reno}{Thesis: "Overexpression of DGAT1 and Modified Cysteine Soy Oleosin Increases Oil Content in the Green Tissue of \textit{Arabidopsis thaliana}", also earned a minor in mathematics.\\GPA: 3.402}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}


%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

\section{Achievements}

\begin{twenty} % Environment for a short list with no descriptions
	\twentyitem{2016}{Secretary \& Director}{Reno Video Game Symphony}{Designed \& implemented a constitution for the Reno Video Game Symphony and made the organization 501(c)(3) nonprofit.}
	\twentyitem{2014}{Eagle Scout}{Boy Scouts of America}{Eagle scout project was painting a map of the United States at Virginia Palmer Elementary School.}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 PROJECTS
%----------------------------------------------------------------------------------------

% \section{Projects by Release Date}

% \begin{twenty} % Environment for a short list with no descriptions
% 	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
% 	\twentyitem{in progress}{Develop Biology}{\href{https://develop,bio}{https://develop.bio}}{Open source, backwards compatible, recursive hypergraph with reflection and a frontend as my own programming language.}
% 	\twentyitem{2021}{Eons Basic Build System}{\href{https://github.com/eons-dev/bin\_ebbs}{https://github.com/eons-dev/bin\_ebbs}}{Python devops with runners for any process \& any language.}
% 	% \twentyitem{2021-2022}{Mood Recorder}{\href{https://moodrecorder.org}{https://moodrecorder.org}}{Progressive Web App for improving emotional health.}
% 	\twentyitem{2020}{Web Infrastructure}{\href{https://web.infrastructure.tech/architecture/}{https://web.infrastructure.tech/architecture/}}{Globally distributed Kubernetes cluster \& auto-managed WordPress.}
% \end{twenty}

%----------------------------------------------------------------------------------------
%	 OTHER INFORMATION
%----------------------------------------------------------------------------------------

\section{Latest}

Get the latest version of this resume at \href{https://github.com/eons44/resume.doc}{https://github.com/eons44/resume.doc}\\
\textbf{References are available upon request} (they will not be stored on the public repo).

\end{document} 
